Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
...

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s = \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	number of neurons per cluster $l$

	number of clusters $c$

	number of erased clusters $c_e$

	number of messages : $m$

	number of activities per cluster : $a$

	density : $d$

@@

	\[ d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m \]

@@

	The network is a symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $. The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.

@@

	$\eta_{max} = \max_x \eta_x $

	\subsubsection{Simulations}
		Theoretical and empirical densities match very closely, see Figure \ref{densiteth} %gap of theoretical density with density in simulations : under $1$ percent,

		The variant rule improves the retrieval rate for multiple iterations and/or corrupted messages.

		The simulations agree with the analytical results for both density and error rate.

	For one iteration (for erasures, not for errors), winner takes all is the same as $a$-winners take all.

	For multiple iterations $a$-winners take all is a significant improvement.

	See Figure \ref{erasuresth}

		"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
			\label{densiteth}
	\end{figure}

@@

		\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
	\end{figure}

	\newpage
	p
	\newpage
	$\,$
	\newpage

@@

	Knowing the density of the network, we can compute the laws for scores achieved by different neurons in different clusters. Subscript $g$ will indicate a neuron being part of the message (it should be activated), subscript $b$ the contrary (the neuron should not be activated). Subscript $a$ means the neuron is activated. Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
	Being connected to a given activated neuron occurs with probability $d$. However corrects neurons see their scores shift, as well as activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$. We can express those probability laws as :

@@

	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$

@@

	\newpage

@@

	To be really precise : (ne pas oublier de tenir compte changement des lois, formule inexacte pour l'instant)
	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
	\end{align*}

@@

	See \ref{corruptth}

@@

	\subsubsection{Simulations}
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\label{corruptth}
	\end{figure}

@@

>>>>

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	%number of neurons per cluster $l$

	%number of clusters $c$

	%number of erased clusters $c_e$

	%number of messages : $m$

	%number of activities per cluster : $a$

	%density : $d$

@@

	\begin{align}
		\label{formula_density}
		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m 
	\end{align}

@@

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $. The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.

@@

	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $.

	\subsubsection{Simulations}
		Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent,

		Simulations agree with the analytical results for error rate, see Figure \ref{erasuresth}.

	For one iteration (for erasures, not for errors), "winner takes all" is the same as "$a$-winners take all".

	For multiple iterations $a$-winners take all is a significant improvement.
	%The variant of the rule significantly improves the retrieval rate over multiple iterations. (For one iteration, is is the same as taking only maximum scores.)

	%See Figure \ref{erasuresth}

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
			\label{densiteth}
	\end{figure}

@@

		Figure \ref{comperth} shows improvements in capacities over unipartite cliques network. The more the problem is difficult, the more redundancies introduced by multipartite cliques are useful.

		\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
		\label{comperth}
	\end{figure}
%	
%	\newpage
%	$\,$
%	\newpage
%	$\,$
%	\newpage

@@

	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute the laws of probabilities for scores achieved by different type of neurons in different clusters. We can divide neurons in 5 groups. Subscript $g$ will indicate a neuron being part of the message (it should be activated), subscript $b$ the contrary (the neuron should not be activated). Subscript $a$ means the neuron is already activated. Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
	Being connected to a given activated neuron in a corrupted cluster occurs with probability $d$, since errors are identically distributed. Moreover corrects neurons see their scores shift, as do all activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$. We can express those probability laws as :

@@

	Activated neurons benefits of the memory effect $\gamma$ :	
	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$

@@

@@

%	To be really precise : (ne pas oublier de tenir compte changement des lois, formule inexacte pour l'instant)
%	\begin{align*}
%	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
%	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
%	\end{align*}

@@

@@

	\subsubsection{Simulations}
	See Figure \ref{corruptth}
	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\label{corruptth}
	\end{figure}

@@

		Multipartite cliques don't improve theoretical efficiency (for not accepting messages that weren't previously seen by the network)
